---
title: "Getting started with binomial"
author: "Soo Young Shin"
date: "4/30/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution

The binomial distribution is the most famous probability distribution among discrete random variables.

The pakage "binomial" perform the functions to calculate the probabilities about the number of successes in a fixed number of random identical trials.

And this package also calculate related properties of binomial random variable.


## characteristic of Binomial Variable

1. Valid input for the 'prob' is a number between 0 and 1. 

2. Valid input fot the 'trials' is a non-negative integer number.

3. Valid input for the 'success' is a number of integer greater than or equal to 0 and less than or equal to the number of trials.

If ypu put invalid input, you get an error message.



## Binomial Functions

### Creating Binomial Variable

To create a binomail object, you can use 'bin_variable()' function.

For example, you are tossing a fair coin 5 times.

```{r}
coin <- bin_variable(5, 0.5)
coin
```

### bin_choose()

The 'bin_choose()' function takes input of success and trials to calculate the number of combination in which 'k' successes in 'n' trials. 

```{r}
bin_choose(n = 5, k = 3)
bin_choose(n = 5, k = 0)
bin_choose(n = 5, k = 0:3)
```


###bin_probability()

The 'bin_probability()' function takes input of success, trials, prob to calculate the probability of getting k successes in n trials for a binomial random variable.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5 )
bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_probability(55, 100, 0.45)
```


###bin_distribution()

The 'bin_distribution()' function takes input of trials, prob to list the probabality of each successe with probability p in n trials

```{r}
dist <- bin_distribution(trials = 5, prob = 0.5)
dist
```

###plot.bindis()

The function 'plot.bindis()' graphs a barplot to display the probability histogram of a binomial distribution.


```{r}
dist <- bin_distribution(trials = 5, prob = 0.5)
plot(dist)
```

  

###bin_cumulative

The function 'bin_cumulative' list the cumulative probabality of each successe with probability p in n trials.

```{r}
cum <- bin_cumulative(trials = 5, prob = 0.5)
cum
```


###plot.bincum()

The function 'plot.bincum()' graphs the cumulative distribution.

```{r}

cum <- bin_cumulative(trials = 5, prob = 0.5)
plot(cum)

```



###summary of the binomial variable

Use `summary()` to get a full summary of description of a binomial variable object

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
binsum1 <- summary(bin1) 
binsum1

```

##Functions of measure

###bin_mean()

The function "bin_mean()" gives expected value of object.

```{r}
mean <- bin_mean(10, 0.3)
mean
```



###bin_variance()

The function "bin_variance()" gives the variance of a binomal distribution.

```{r}
var <- bin_variance(10, 0.3)
var
```



###bin_mode()

The function "bin_mode()" gives the mode of a binomal distribution.

```{r}
mode <- bin_mode(10, 0.3)
mode
```



###bin_skewness()

The function "bin_skewness()" gives the skewness of a binomal distribution.

```{r}
skewness <- bin_skewness(10, 0.3)
skewness
```



###bin_kurtosis()

The function "bin_kurtosis()" gives the kurtosis of a binomal distribution.

```{r}
kurtosis <- bin_kurtosis(10, 0.3)
kurtosis
```
