---
title: "Getting started with binomial"
author: "Soo Young Shin"
date: "4/30/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution

The binomial distribution is the most famous probability distribution among discrete random variables.

The pakage "binomial" perform the functions to calculate the probabilities about the number of successes in a fixed number of random identical trials.

And this package also calculate related properties of binomial random variable.


## characteristic of Binomial Variable

1. Valid input for the 'prob' is a number between 0 and 1. 

2. Valid input fot the 'trials' is a non-negative integer number.

3. Valid input for the 'success' is a number of integer greater than or equal to 0 and less than or equal to the number of trials.

If ypu put invalid input, you get an error message.



## Binomial Functions

### Creating Binomial Variable

To create a binomail object, you can use 'bin_variable()' function.

For example, you are tossing a fair coin 5 times.

```{r}

coin <- bin_variable(5, 0.5)
coin

```
